---
title: Twilight Label
format: html
editor: visual
---

```{r, setup}
# Choose the id 
id <- "CG181"

# Set the directory to the project root
knitr::opts_knit$set(root.dir = "..")
library(GeoPressureR)
library(ggplot2)
library(glue)
```

## Create tag

Start from an existing `tag`

```{r}
load(glue("/Users/sjs7465/Documents/GitHub/myrtle_geo_pressure/data/interim/pressure_only/{id}.RData"))
```

or generate from a new ones

```{r, eval=F}
tag <- tag_create(config::get("id", id),
  crop_start = config::get("crop_start", id),
  crop_end = config::get("crop_end", id)
) |>
  tag_label() |>
  tag_set_map(
    extent = config::get("extent", id),
    scale = config::get("scale", id),
    known = config::get("known", id)
  )

```

## Create Twilight

Generate the twilight automatically. Check that `twl_offset` allows for night/day being centered on the figure, otherwise edit accordingly

```{r}
tag <- twilight_create(
  tag,
  twl_offset = config::get("twl_offset", id)
)

plot(tag, type = "twilight")
```

## Annotate twilight

```{r}
twilight_label_write(tag, file=glue::glue("/Users/sjs7465/Documents/GitHub/myrtle_geo_pressure/data/twilight-label/{tag$param$id}.csv"))
```

Read and check the twilight annotation

```{r}
tag <- twilight_label_read(tag, file=glue::glue("/Users/sjs7465/Documents/GitHub/myrtle_geo_pressure/data/twilight-label/{tag$param$id}-labeled.csv"))
plot(tag, type = "twilight")
```

## Compute likelihood map

```{r}
tag <- geolight_map(tag)
```

`twl_calib_adjust` and `twl_llp` can generally be left to default, but add to `config.yml` if needed.

## Check

### Check calibration

```{r}
barW <- median(diff(tag$param$twl_calib$x)) / 2
plot(tag$param$twl_calib)
rect(xleft = tag$param$twl_calib$x - barW, ybottom = 0, xright = tag$param$twl_calib$x + barW, ytop = tag$param$twl_calib$y, col = gray(0.5))
lines(tag$param$twl_calib, col = "red")
```

### Check light map

```{r}
plot(tag, type = "map_light")
```

### Check with pressure and trajectory

```{r, eval=F}
geopressureviz(tag)
```
